---
title: "STAT 4130: Homework4"
author: "Wang Boqian"
date: '2023-07-19'
output: pdf_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# if you are using libraries, it's good practice to load them here
library(ggplot2)
library(car)
library(tibble)
library(locfit)
```

## Question 1

```{r}
# please do your coding inside a code chunk
# unless otherwise stated, feel free to do all computations in R
# commented code is always appreciated

#print("Hello")
# 1a
# Simple Linear Regression
df <- read.csv("hw4.csv")
lm1 = lm(y ~ x,data = df)
# Residual Plot
ggplot(df, aes(x=1:15, y=lm1$res)) + geom_point() + geom_line() + xlab("t") + ylab("Residuals")+ geom_hline(yintercept=0)

# 1b
# DW Test
durbinWatsonTest(lm1, alt="positive")

# 1c
# Cochrane–Orcutt Iteration
x = df$x
y = df$y
n = length(y)
res = lm1$res
rho.hat = sum(res[1:(n-1)]*res[2:n]) / sum(res*res)
ystar = y[2:n] - rho.hat*y[1:(n-1)]
xstar = x[2:n] - rho.hat*x[1:(n-1)]
lm2 = lm(ystar ~ xstar)
summary(lm2)

# 1d
# DW Test
durbinWatsonTest(lm2, alt="positive")
```

#### 1a. 
The time-plot shows quite smooth, which indicates a sign of positive autocorrelation.

#### 1b. 
Since the p-value = 0.003 < 0.05, we reject H0 and accept H1: There is a positive autocorrelation.

#### 1c.
According to the summary table, the standard error for intercept is 0.55421, and the standard error for slope is 0.01403.

#### 1d,
It has not been successful. Although the p-value is increased from 0.003 to 0.011, it's still far less than 0.05, where we still reject H0 and accept H1: There is a positive autocorrelation. We still need more iterations to reduce the autocorrelation.

## Question 2
```{r problem2Code}
# Your code
# 2a
data <- tibble(
discount = c(5,7,9,11,13,15,17,19,21,23,25),
size = c(500,500,500,500,500,500,500,500,500,500,500),
redeem = c(100,122,147,176,211,244,277,310,343,372,391)
)
lm3 <- glm(redeem ~ discount, data = data, family = gaussian())
summary(lm3)

# 2c
plot(data$discount,data$redeem)
abline(lm3)

# 2d
lm4 <- glm(redeem ~ discount + I(discount^2), data = data, family = gaussian())
summary(lm4)

# 2e
plot(data$discount,data$redeem)
abline(lm3)
abline(lm4)

# 2f
confint(lm4)
```

#### 2b
According to the summary table of lm3, we can calculate the R-squared, which equals to 0.997, which is close to 1. So we can't claim that the logistic regression model from part a is not adequate.

#### 2d
According to the summary table of lm4, we found that the p-value of the quadratic term = 0.620 >> 0.05. So this quadratic term is not required in the model as there is no strong evidence of non-linearity.

#### 2e
Yes, as the plot suggests, lm3 obviously underestimates most of the data, while data points in lm4 distributes more evenly.

## Question 3
```{r problem3Code}
# Your Code
# 3a
data(mine)
data2 = mine
lm5 <- glm(frac ~ inb + extrp + seamh + time, data = data2, family = poisson(link = "log"))

# 3c
confint(lm5)

# 3d
lm6 <- glm(frac ~ inb + extrp, data = data2, family = poisson(link = "log"))
anova(lm5,lm6, test = "LRT")

# 3e
plot(lm5, which = 1)
plot(lm6, which = 1)
```

#### 3b
According to the summary table of lm5, we can calculate the R-squared, which equals to 0.4951. This indicates that the model can interpret less than 50% of the data points, which is far from our satisfaction.

#### 3d
lm5 is reduced to lm6 by removing the variable "seamh" and "time" because their p-values are larger than 0.05. I found that the p-value of the Analysis of Deviance is 0.1202 > 0.05, which indicates that the reduced model(lm6) is preferred.

#### 3e
Not really. Simply deleting features does not make the figure satisfactory from a residual analysis viewpoint. Variable transformations and interactions should be taken into account to modify the model.

